---
title: "R Notebook"
output: html_notebook
---


Load libraries and spreadsheet


NOTE: make a duplicate of the excel sheet and make it into a csv

change name and path of spreadsheet in read_csv command
```{r}
library(dplyr)
library(openxlsx)
spreadsheet<- read_csv("Path_to_csv")

```
Recode Guidelines:
RAW role code	RAW role	RECODE role code	RECODE role
8	Teacher	1	Teacher
9	SPED Teacher	1	Teacher
13	School-Based Law Enforcement	2	School-based law enforcement
14	Security	2	School-based law enforcement
5	Mental Health or Behavior Coordinator	3	Student Support and Health
10	Nurse	3	Student Support and Health
11	Social Worker	3	Student Support and Health
12	Counselor	3	Student Support and Health
1	Superintendent	4	Leadership
2	Assistant Superintendent	4	Leadership
6	Principal	4	Leadership
7	Assistant Principal	4	Leadership
3	Safety & Security Director	5	Safety and Security
4	Emergency Management Coordinator	5	Safety and Security
15*	Other district role*	6	Other
16*	Other campus role*	6	Other
15**	Other district/campus role	7	Administration
16**	Other district/campus role	7	Administration
			
15* Other district role – Review role text and categorize accordingly	*Librarian, Paraprofessionals, and Interventionist recoded as Teacher (1)
16* Other campus role – Review role text and categorize accordingly		
			
15**		**Higher level positions that are not SI, Asst SI, Principal, or Asst Principal. 
16**		**Higher level positions that are not SI, Asst SI, Principal, or Asst Principal. 


```{r}
spreadsheet <- spreadsheet %>%
  mutate(
    `Current Role` = case_when(
      `Current Role` %in% c(8, 9) ~ 1, # 8 and 9 recode as 1
      `Current Role` %in% c(13, 14) ~ 2, #13 and 14 recode as 2, etc
      `Current Role` %in% c(5, 10, 11, 12) ~ 3,
      `Current Role` %in% c(1, 2, 6, 7) ~ 4,
      `Current Role` %in% c(3, 4) ~ 5,
      `Current Role` == 16 & grepl("intervention", `Other Camp Role`, ignore.case = TRUE) ~ 1, # if column contains number 16 and other column contains the word intervention, ignoring case, replace with 1
      `Current Role` == 15 & grepl("intervention", `Other Dist Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 16 & grepl("behavior", `Other Camp Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 15 & grepl("behavior", `Other Dist Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 16 & grepl("psycholog", `Other Camp Role`, ignore.case = TRUE) ~ 3,
      `Current Role` == 15 & grepl("psycholog", `Other Dist Role`, ignore.case = TRUE) ~ 3,
      `Current Role` == 16 & grepl("LSSP", `Other Camp Role`, ignore.case = TRUE) ~ 3,
      `Current Role` == 15 & grepl("LSSP", `Other Dist Role`, ignore.case = TRUE) ~ 3,
      `Current Role` == 16 & grepl("director", `Other Camp Role`, ignore.case = TRUE) ~ 7,
      `Current Role` == 15 & grepl("director", `Other Dist Role`, ignore.case = TRUE) ~ 7,
      `Current Role` == 16 & grepl("librarian", `Other Camp Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 15 & grepl("librarian", `Other Dist Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 16 & grepl("paraprof", `Other Camp Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 15 & grepl("paraprof", `Other Dist Role`, ignore.case = TRUE) ~ 1,
      `Current Role` == 16 & grepl("principal", `Other Camp Role`, ignore.case = TRUE) ~ 7,
      `Current Role` == 15 & grepl("principal", `Other Dist Role`, ignore.case = TRUE) ~ 7,
      TRUE ~ `Current Role` # if something is not mentioned, still keep it
    )
  )

spreadsheet # look at spreadsheet

```

Export as an xlsx, whatever the end of the path is will be its new name
```{r}
write.xlsx(spreadsheet, "path_to_newly_saved_xlsx")
```


